The pollination trade-off

### 2018-08-19 paper/supp-info.Rmd
Move scatter plot community vs global to its own function
Issue #6

```{r fig-global-community-correlations, fig.height = 2.5, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level."}
drake::loadd(plant_rel_abu, plant_pheno_overlap, degree, sites)

ab <- plant_rel_abu %>%
  dplyr::select(-abu) %>%
  dplyr::rename(value = rab) %>%
  dplyr::mutate(term = "rab")

ph <- plant_pheno_overlap %>%
  dplyr::rename(value = tov) %>%
  dplyr::mutate(term = "tov")

k <- degree %>%
  dplyr::select(-kn) %>%
  dplyr::rename(value = k) %>%
  dplyr::mutate(term = "k")

dplyr::bind_rows(ab, ph, k) %>%
  dplyr::filter(var_trans == "log") %>%
  tidyr::spread(scale, value) %>%
  humanize(sites) %>%
  ggplot(aes(x = community, y = global)) +
  geom_smooth(method = "lm", colour = "black", size = 0.75) +
  geom_hline(yintercept = 0, size = 0.25, linetype = 2) +
  geom_vline(xintercept = 0, size = 0.25, linetype = 2) +
  geom_point(shape = 21, size = 1) +
  facet_wrap( ~ term, scales = "free") +
  coord_equal() +
  pub_theme()
```

>>>>

```{r fig-global-community-correlations, fig.height = 2, fig.cap = "Relationship between the model's independent variables calculated at the community level and at the study-wide level."}
drake::readd(fig_community_global_scatter)
```
